Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound

### 2019-01-07 ongoing/report/sec_1_introduction.tex
Shorten introduction

\(|a|\) denotes the magnitude for real or complex numbers \(a\).
The real and imaginary part of \(a\) will be denoted respectively as \(\MF{Re}(a)\) and \(\MF{Im}(a)\), respectively, thus \(a =\MF{Re}(a) + i \MF{Im}(a)\)

@@

In our context, the complex numbers has natural interpretation as the phasor of electronic waves.
Of course, scalar operation on \(\MB{R}^N\) is over field \(\MB{R}\), and that on \(\MB{C}^N\) is over field \(\MB{C}\).
We use \(\MB{K}\) to refer to either \(\MB{R}\) or \(\MB{C}\).
Not to avoid confusion, we call the Hilbert space \(\MB{K}^N\) over \(\MB{K}\) to be \(\MB{V}_{\MB{K}} (N)\).
We also call the collection of \(M\) by \(N\) matrices to be \(\MB{M}_{\MB{K}}(M,N)\), and its role as linear transformation is understood.
Inner product of \(\V{a}\) and \(\V{b}\) is denoted as \(\IP{ \V{a}, \V{b} }\).
Slightly abusing notation, we denote as \(\V{a}(n)\) the \(n\)-th component of \(\V{a}\), and denote as \(\V{A}(m,n)\) the \((m,n)\)-entry of \(\V{A}\)
Particularly, \(\V{u}_n\) is the \(n\)-th unit vector in the Cartesian coordinates (not to be confused with the noise).
\(\|\V{a}\|_p\) denotes the \(\ell_p\)-norm of vector \(\V{a}\).
Recall that \(\ell_\infty\)-norm is the maximum-magnitude norm.

Denote as \(\MB{P}(X)\) the probability, and \(\MB{E}(X)\) the expectation.
Since our discussion involving the entire communication system will get very complicated, we may spell out the dependence of event space index on random variables.

@@

To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \(N_p\) is much larger than the number of measurements \(N_m\).
Here, we consider
%
\Disp{
N_p \gg N_m
}
In such case of insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \(N_p\) parameters?
Of course, more assumption must be made to make the question meaningful.
Any two vectors of parameters differing an element in the null space of the sensing matrix will produce the same measurement.

@@

\Result
{Definition}
{
\(x \in \MB{V}_{\MB{K}} (N_m)\) is called \(s\)-sparse with support \(\MC{A}\), \(s \in \MB{N_m}\), if there is \(\MC{A} \subset T (N_m)\) such that
%
\Disp{ 
x_{T (N) -\MC{A}} =\V{0}
}
with
\Disp{ 
\# \MC{A} \leq s.
}
%
That is, only at most \(s\) components of vector \(x\) is nonzero.
}

\Result
{Program}
{
Let \(A,y\) be given.
Find \(x\) with
%
\Disp{
\min_{x' \in \MB{V}_\MB{K}(K)}
\quad \|x'\|_1
\quad \RM{s.t.} \quad A x' =y
}
%
}

\Result
{Theorem}
{
Let \(y =Ax\).
Suppose \(x\) is \(s\)-sparse, then the program () completely recovers \(x\).
That is, a noiseless linear transformation of a sparse vector is completely recovered by a \(\ell_1\)-minization program with an overwhelming probability, if
%
\Disp{
\delta_{S} +\delta_{2S} +\delta_{3S} <1
}
%
}

\Result
{Definition}
{
Let \(A\) be an \(n \times p\) matrix, with
%
\Disp{
\delta_{S} +\delta_{2S} +\delta_{3S} <1
}
%

having unit \(\ell_2\)-norm columns.
For each integer \(S \in \MB{N}\), we say that \(A\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(x\) with \(\|x\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
%
\Disp{
(1-\delta_S) \|x\|^2
\leq \|A_T x\|_2^2
\leq (1+\delta_S) \|x\|^2
}
%
}

RIP of order \(S\) is essentially saying that the matrix \(X\) is ``almost isometry'' up to ``relative error'' \(\delta_S\).

Moreover, for \(T,T' \subset \{1, \dotsc, p \}\), let \(\vartheta_{S,S'}\) be the smallest constant such that
%
\Disp{
| \IP{ X_T c, X_{T'} c' } |
\leq \vartheta_{S,S'} \cdot \| c \|_2 \|c'\|_2
}
%

For concreteness, consider a linear transformation with noise,
%
\Disp{
y =Ax + z
}
%
where \(z\) is an i.i.d., zero-mean, \(\sigma\)-variance AWGN vector.
How can we hope to estimate \(h\) when, in addition to insufficient observations, there are too few observations?

\Result
{Program}
{
Let \(A,y\) be given.
Find \(x\) with
%
\Disp{
\min_{x' \in \MB{K}^p}  \|\hat{x'}\|_1 \\ \NT
\RM{subject}\; \RM{to} \quad \|A^\H r\|_\infty \leq \lambda_p \sigma
}
%
where \(r =y -A \hat{x}\).
}
And it can be shown that this \(\ell_\infty\)-constraint problem may be recast as a linear program.

\subsection{Condition of RIP Linear Transformation}

The constant \(\delta\) in the proof of DS is significant.
Indeed, we may observe that in theorem (), the bound is not tightest when \(\delta=0\), i.e., that \(A\) is fully unitary.

Here, it is not clear at first what matrices serves as the RIP condition.
But later, Baraniuk (2008) have found there is a particularly convenient sufficient condition to verify RIP.

\Result
{Theorem}
{
Let each entry of random matrix \(A \in \MB{V}_\MB{K}(M \cdot N)\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\sqrt{M}\) (that is, Rademacher distribution).
Then, with \(0 <\epsilon <1\),
%
\Disp{
   \MB{P}( |\|Ax\|_2^2 -\|x\|_2^2| \geq \epsilon \|x\|_2^2)
   \leq 2 \exp (-n c_0(\epsilon))
}
%
where we have
%
\Disp{
c_0(\epsilon)
=\epsilon^2/4 -\epsilon^3/6.
}
%
}

@@

To explain the idea, consider a simplified scenario.
Let \(x[t] \in \MB{R}^N\) be random instances of i.i.d.\ Rademacher distribution.
Consider a linear time-invariant channel with
%
\Disp{
y[t] =(x[t] \star h[t]) + z[t]
}
%
where \(h[t] \in \MB{R}^L\) is the channel's impulse response, \(x[t] \in \MB{R}^N\) as the input, \(y[t] \in \MB{R}^N\) as the output, and \(z[t] \in \MB{R}^L\) are random instances of i.i.d.\ normalized AWGN, and \(N \gg L\).
Here, if the convolutional relation is expressed by a matrix \(X\), \(X\) is a Toeplitz matrix, so that
%
\Disp{
y =X h
}
%
where \(X\) takes the form
%
\Disp{
X
=\begin{bmatrix}
x_1, &0, &\cdots, &0 \\
x_2, &x_1, &\cdots, &0 \\
\vdots, &\vdots, &\ddots, &0 \\
x_N, &x_{N-1}, &\cdots, &x_1
\end{bmatrix}
}
%
We seek to get \(h\) in this undertermined system.

Bajwa et.\ al.\ was able to show that \(X\) is RIP of overwhelmingly probability.

@@

The setting here is \(y =Ax\), the noiseless, real-number case.
Same as before, let \(y \in \MB{V}_\MB{K}(M)\), \(x \in \MB{V}_\MB{K}(N)\) which is \(s\)-sparse, while \(M \ll N\).
We pick up the columns of \(A\) greedily, hoping to correspond to the support of \(x\).

@@

@@

For the proof, see the technical report: Tropp and Gilbert (2007a).

It is interesting to note that, ever since, the direct application of \(\ell_1\)-problem following the orignal Cand\`es-and-Tao approach has been seemingly rare.
Scholars has applied OMP in favor of DS, in the ease of implementation of the former, and OMP becomes perhaps the most widely used channel estimation technique.
To see this, let \(\M{F}\) be the precoder and \(\M{W}\) the combiner, and \(\M{H}\) the channel, and consider the noiseless case.
Let signal \(x\) be sent, and \(y\) be receiverd, that is
%
\Disp{
   \V{y} =\M{W} \M{H} \M{F} \V{x}
}
%

\Result
{Definition}
{
Define \(\RM{vec}(\M{A}) \in \MB{K}^{nm}\) to be the vectorization of \(\M{A} \in \MB{M}_{\MB{K}}(n,m)\).
}

\Result
{Definition.}
{
For \(\RM{vec}(A) \in \MB{M}_{\MB{K}}(n,m)\) and \(\RM{vec}(A) \in \MB{M}_{\MB{K}}(n,m)\)
Define the Kronecker product \(\RM{vec}(A) \in \MB{K}^{nm}\) 
}

With (), scholars often exploit the relation
%
\Disp{
\RM{vec}(Y)
=\big[ (F^\H) \otimes W \big] \RM{vec}(\M{H})
}
%

@@

Our contribution include:

\begin{enumerate}
\item As a \textit{prima face} difference, we use a modified DS rather than OMP, done on the beamspace rather than the spatial domain, and involving complex numbers rather than real numbers.
\item We do not assume that the virtual channel model is naturally quantized in its angle of departure and of arrival, thus removes concern of the quantization error within the proof.
\item Accordingly, the effect of quantization of the virtual channel's phase angle incorporated in the beambook has been especially considered in the bound.
\item Moreover, an explicit bound has been shown to provide realistic guide for engineering, where the sparsity of the virtual channel matrix, rather than just assumed, is written out as a function of the number of paths of the channel.
\item We derive explicitly the SOCP problem and afterwards its dual problem, and wrote a proof-of-concept but efficient code.
\end{enumerate}

>>>>

\(|a|\) denotes the magnitude for real or complex numbers \(a\).
The real and imaginary part of \(a\) will be denoted respectively as \(\MF{Re} (a)\) and \(\MF{Im} (a)\), respectively, thus \(a =\MF{Re} (a) + i \MF{Im} (a)\)

@@

In our context, the complex numbers has natural interpretation as the phasor of electronic waves.
Of course, scalar operation on \(\MB{R}^N\) is over field \(\MB{R}\), and that on \(\MB{C}^N\) is over field \(\MB{C}\).
We use \(\MB{K}\) to refer to either \(\MB{R}\) or \(\MB{C}\).
Not to avoid confusion, we call the Hilbert space \(\MB{K}^N\) over \(\MB{K}\) to be \(\MB{V}_{\MB{K}} (N)\).
We also call the collection of \(M\) by \(N\) matrices to be \(\MB{M}_{\MB{K}} (M,N)\), and its role as linear transformation is understood.
Inner product of \(\V{a}\) and \(\V{b}\) is denoted as \(\IP{ \V{a}, \V{b} }\).
Slightly abusing notation, we denote as \(\V{a} (n)\) the \(n\)-th component of \(\V{a}\), and denote as \(\V{A} (m,n)\) the \((m,n)\)-entry of \(\V{A}\)
Particularly, \(\V{u}_n\) is the \(n\)-th unit vector in the Cartesian coordinates (not to be confused with the noise).
\(\|\V{a}\|_p\) denotes the \(\ell_p\)-norm of vector \(\V{a}\).
Recall that \(\ell_\infty\)-norm is the maximum-magnitude norm.

Denote as \(\MB{P} (X)\) the probability, and \(\MB{E} (X)\) the expectation.
Since our discussion involving the entire communication system will get very complicated, we may spell out the dependence of event space index on random variables.

@@

To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \(N_p\) is much larger than the number of measurements \(N_m\).
Here, we consider
%
\Disp{
N_p \gg N_m
}
%
In such case of insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \(N_p\) parameters?
Of course, more assumption must be made to make the question meaningful.
Any two vectors of parameters differing an element in the null space of the sensing matrix will produce the same measurement.

@@

\Result
{Definition}
{
\(h \in \MB{V}_{\MB{K}} (N_m)\) is called \(s\)-sparse with support \(\MC{A}\), \(s <N_m\), if there is \(\MC{A} \subset T (N_m)\) such that
%
\Disp{ 
x_{T (N) -\MC{A}} =\V{0}
}
with
\Disp{ 
\# \MC{A} \leq s.
}
That is, only at most \(s\) components of vector \(x\) is nonzero.
}

\Result
{Program}
{
Let \(P \in \MB{M}_\MB{K} (N_m, N_p)\) and \(y \in \MB{V}_\MB{K} (N_p)\) be given.
Find \(h \in \MB{V}_\MB{K} (N_p)\) with
%
\Disp{
\min_{h'}
\quad &\|h'\|_1 \\
\quad \RM{subject}\; \RM{to}
\quad &P h' =y
}
}

Now let \(y =P h\).
Suppose \(h\) is \(s\)-sparse, then the program () completely recovers \(h\).
That is, a noiseless linear transformation of a sparse vector is completely recovered by a \(\ell_1\)-minization program with an overwhelming probability.

\Result
{Definition}
{
Consider \(P \in \MB{M}_{\MB{K}} (N_m, N_p)\), with unity-\(\ell_2\)-norm columns.
For \(s =1, \dotsc N_p\), we say that \(P\) satisfies the RIP of order \(s\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(x\) with \(\|x\|_0 \leq s\), for all \(\MC{T} \subset T(N_m)\) with \(|\MC{T}| \leq s\),
%
\Disp{
(1-\delta_s) \|h\|^2
\leq \|P_{\MB{T}} h\|_2^2
\leq (1+\delta_s) \|h\|^2
}
}

RIP of order \(s\) is essentially saying that the matrix \(X\) is ``almost unitary'' up to ``relative error'' \(\delta_s\).

Consider a linear transformation with noise corruption,
%
\Disp{
\V{y} =\M{P} \V{h} + \V{z}
}
%
where (w.l.o.g.) \(z\) is an i.i.d.\ normalized Gaussian vector.
How can we hope to estimate \(h\) when, in addition to insufficient observations, there are too few observations?

\Result
{Program}
{
Let \(\M{P} \in \MB{V}_\MB{R} (N_m, N_p)\) and \(\V{y} \in \MB{V}_\MB{R} (N_m)\) be given.
Find \(\V{h} \in \MB{V}_\MB{R} (N_m)\) with
%
\Disp{
\min_{\V{h}'} \quad &\|\V{h}'\|_1 \\ \NT
\RM{subject}\; \RM{to} \quad &\|\M{P}^\H (\M{P} \V{h} -\V{y})\|_\infty \leq \gamma
}
}

And it can be shown that this \(\ell_1\)-minimization problem with \(\ell_\infty\)-constraint may be recast as a linear program (LP), lending convex programming technique applicable.
Note that they confined their discussion for real vectors.

\subsection{Sufficient Conditions of RIP}

The constant \(\delta\) in the proof of DS is significant.
Indeed, we may observe that in theorem (), the bound is not tightest when \(\delta=0\), i.e., that \(P\) is fully unitary, rendering the RIP an important role.
Here, it is not clear at first what matrices serves as the RIP condition.

But later, Baraniuk (2008) have found there is a particularly convenient sufficient condition to verify RIP.

\Result
{Theorem}
{
Let each entry of random matrix \(P \in \MB{M}_\MB{K} (N_m, N_p)\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\sqrt{N_m}\) (that is, Rademacher distribution).
Then, with \(0 <\epsilon <1\),
%
\Disp{
   \MB{P} ( |\|P h\|_2^2 -\|h\|_2^2| \geq \epsilon \|h\|_2^2)
   \leq 2 \exp (-n (\epsilon^2/4 -\epsilon^3/6) )
}
}

@@

To explain the idea, consider a linear time-invariant channel that \(y(t) =(x \star h)(t) + z(t)\), where \(x(t)\) is random instances of i.i.d.\ Rademacher distribution drawn in each time index, \(h(t)\) is the channel's impulse response, \(y(t)\) as the output, and \(z(t)\) is i.i.d.\ normalized AWGN
Simply assuming \(h\) has sparse support, and let the convolution with \(x\) be expressed by a matrix \(X\), \(X\) is a Toeplitz matrix, so that \(y =X h +z\).
Then Bajwa et.\ al.\ was able to show that, \(X\) is RIP of overwhelmingly probability, and DS is ready to be applied, with some nice bounds on its performance drawing from Cand\`es and Tao's theorems.

@@

Same as before, consider \(\V{y} \in \MB{V}_\MB{K} (N_p)\), \(\V{h} \in \MB{V}_\MB{K} (N_s)\), where \(\V{h}\) is \(s\)-sparse, with \(N_p \gg N_s\).
If
\Disp{
\V{y} =\M{P} \M{h},
}
that is, the noiseless, real-number case.
We pick up the columns of \(\M{P}\) greedily, hoping to correspond to the support of \(\V{h}\).

@@

From Tropp and Gilbert (2007a),

@@

It is interesting to note that, ever since, scholars has applied OMP in favor of DS, due the simplicity of former's implementation, making OMP perhaps the most widely used channel estimation technique.

For concreteness, let \(\M{F}\) be the precoder and \(\M{W}\) the combiner, and \(\M{H}\) the channel, and consider the noiseless case.
Let signal \(\V{x}\) be sent, and \(\V{y}\) be receiverd, that is
%
\Disp{
\V{y} =\M{W} \M{H} \M{F} \V{x}
}
%

\Result
{Definition}
{
Define \(\RM{vec} (\M{A}) \in \MB{K}^{NM}\) to be the vectorization of \(\M{A} \in \MB{M}_{\MB{K}} (N,M)\).
}

\Result
{Definition.}
{
For \(\RM{vec} (A) \in \MB{M}_{\MB{K}} (N,M)\) and \(\RM{vec} (A) \in \MB{M}_{\MB{K}} (N,M)\)
Define the Kronecker product \(\RM{vec} (A) \in \MB{K}^{nm}\) 
}

With (), scholars often exploit the relation
%
\Disp{
\RM{vec} (Y)
=\big[ (F^\H) \otimes W \big] \RM{vec} (\M{H})
}
%

@@

Our contribution includes:

\begin{enumerate}
\item As a \textit{prima face} difference, we use a modified DS rather than OMP, done on the beamspace rather than the spatial domain, and involving complex numbers rather than real numbers.
\item Moreover, an explicit bound has been shown to provide realistic guide for engineering, where the sparsity of the virtual channel matrix, rather than just assumed, is written out as a function of the number of paths of the channel.
\item Accordingly, the concern of quantization error of the virtual channel's phase angle (which is inevitable when designing the OMP beambook) has already been considered in the proof of our main bound.
\item We derive explicitly the SOCP problem and afterwards its dual problem, and wrote a proof-of-concept but efficient code.
\end{enumerate}

### 2019-01-07 ongoing/report/sec_3_theorems_and_proofs.tex
Shorten introduction

\Result
{Lemma}
{
Let \(\varphi (\omega_h)\) be uniformly, independently distributed in \([0,2\pi)\), and array response \(\V{a} (\varphi)\) defined as in ().
Then
%
\Disp{
\| \V{a} (\varphi) \|_1
\leq \frac{1}{\pi^2} \log \frac{L}{N}.
}
%
}

To find the \(l\)-th path's contribution to the frequency domain, recall the identity for Dirichlet kernel
%
\Disp{
D (\varphi)
:=&\left| \sum_{n=0}^{N-1} \RM{e}^{i n \varphi} \right| \\ \NT
=&\frac{|\sin (N \varphi/2)|}{|\sin (\varphi /2)|},
\quad 0 \leq \varphi \leq \pi
}
%

By taking the first two term of the expansion
%
\Disp{
\sin x =x -x^3/6 + \MC{O}(x^5), \quad x \ll 1
}
%
and noting the monotony of the first two terms,
%
\Disp{
D (\varphi)
\leq& \frac{1}{\varphi/2 -(\varphi/2)^3/6} \NT \\
=& \frac{-48}{\varphi^3 -24\varphi} \\
\quad 0 \leq \varphi \leq \pi,
}
%
The fraction above can be bounded.

By the same token, more generally,
%
\Disp{
\frac{1}{N} S (\pi \varphi')
=&\left| \frac{1}{N} \sum_{n=0}^{N-1} \RM{e}^{-2\pi i k n/N} \RM{e}^{i n \varphi} \right| \NT \\
\leq& \frac{48}{N \pi^3 (\varphi'^3 -24 \varphi' /\pi^2)}
}
%
where \(\varphi' =k/N -\varphi/2\pi\), and the cubic expression is split.
We wish to bound the tail of \(S (\pi \varphi')\), and apply the na\"ive bound
%
\Disp{
&\frac{N}{2\pi} \cdot \frac{48}{N \pi^3} \int_{L/N}^1 \frac{1}{\varphi'^3 -24 \varphi' /\pi^2}
 d\varphi' \NT \\
=&\frac{1}{2\pi^2} \cdot \left( 2 \log \frac{L}{N} +\log \frac{24-\pi^2}{24-\pi^2 L^2 /N^2} \right) \NT \\
\leq& \frac{1}{\pi^2} \log \frac{L}{N}
}
%
Here, the integral in the first line is immediate.
The second term in the bracket is smaller than 0 and is dropped in the last inequality.
The proof of Lemma () is complete.

@@

The rest follows ``The Dantzig Selector'' very closely.

\Result
{Proposition}
{
Let \(h \in \MB{R}^n\) and \(\eta \in \MB{R}^p\) are defined as in ().
Then
%
\Disp{
\|d_{BC}\|_1
\leq \|d_{\MC{A}}\|_1 +\|g_{BC}\|_1
}
%
}

@@

\Result
{Lemma}
{
%
\Disp{
|\IP{ d, P(:, n_h) }|
\leq& 4 \sqrt{\log N_h},
\quad n_h =1, \dotsc, N_h^2.
}
%
}

\Result
{Lemma}
{
%
\Disp{
\|P^\H P d\|_\infty
\leq& 4 \sqrt{\log N_h},
\quad n_h =1, \dotsc, N_h^2.
}
%
}

@@

\Result
{Lemma}
{
%
\Disp{
\|d_{\MC{A}}\|_2
\leq \frac{1}{1-\delta} \|P^\H_{\MC{A}\MC{B}} P d\|_2 +\frac{\delta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
}
%
}

@@

\Result
{Lemma}
{
%
\Disp{
\|d\|_2^2
\leq \|d_{\MC{A}\MC{B}}\|_2^2 +\frac{1}{L} \|d_{\MC{C}}\|_1^2
}
%
}

\subsection{Putting Together}

We can formulate our main theorem.

>>>>

\Result
{Lemma}
{
Let \(\varphi (\omega_h)\) be uniformly, independently distributed in \([0,2\pi)\), and array response \(\V{a} (\varphi)\) defined as in ().
Then
%
\Disp{
\| \V{a} (\varphi) \|_1
\leq \F{1}{\pi^2} \log \F{L}{N}.
}
%
}

To find the \(l\)-th path's contribution to the frequency domain, recall the identity for Dirichlet kernel
%
\Disp{
D (\varphi')
:=&\left| \sum_{n=0}^{N-1} \RM{e}^{i n \varphi'} \right| \\ \NT
=&\F{|\sin (N \varphi'/2)|}{|\sin (\varphi' /2)|},
\quad 0 \leq \varphi' \leq \pi
}
%

Recall the Taylor expansion of sin for the first two terms with respect to zero
%
\Disp{
\sin x =x -\F{x^3}{6} + \MC{O}(x^5), \quad x \ll 1
}
%
Actually it can be shown that we have a inequality
%
\Disp{
\left| x -\F{x^3}{6} \right| \leq \sin x, \quad -\pi \leq x \leq \pi
}
%
Applying the above inequality to the denominator and bounding the nominator by 1, we have
%
\Disp{
\left| D (\varphi') \right|
= \F{48}{|\varphi'^2 -24| |\varphi'|}
\quad 0 \leq \varphi' \leq \pi,
}
%
The fraction above can be bounded.

Particularly,
%
\Disp{
\F{1}{N} S \left( \varphi' -\F{2\pi k}{N} \right)
=&\F{1}{N} \left| \sum_{n=0}^{N-1} \RM{e}^{-2\pi i k n/N} \RM{e}^{i n \varphi} \right| \NT \\
\leq& \F{48}{N \pi^3 (\varphi'^3 -24 \varphi' /\pi^2)}
}
%
where \(\varphi' =k/N -\varphi/2\pi\), and the cubic expression is split.
We wish to bound the tail of \(S (\pi \varphi')\), and apply the na\"ive bound
%
\Disp{
&\F{N}{2\pi} \cdot \F{48}{N \pi^3} \int_{L/N}^1 \F{1}{\varphi'^3 -24 \varphi' /\pi^2}
 d\varphi' \NT \\
=&\F{1}{2\pi^2} \cdot \left( 2 \log \F{L}{N} +\log \F{24-\pi^2}{24-\pi^2 L^2 /N^2} \right) \NT \\
\leq& \F{1}{\pi^2} \log \F{L}{N}
}
%
Here, the integral in the first line is immediate.
The second term in the bracket is smaller than 0 and is dropped in the last inequality.
The proof of Lemma () is complete.

@@

\Result
{Definition}
{
For \(\MC{T}, \MC{T}' \subset \{1, \dotsc, N_p\}\), define the \(s,s'\)-restricted orthogonality constant \(\tau_{s,s'} >0\) to be the smallest such that
%
\Disp{
| \IP{ P_{\MC{T}} h, P_{\MC{T}'} h' } |
\leq \tau_{s, s'} \cdot \| h \|_2 \|h'\|_2
}
}

From ``Decoding from Linear Programming'',
\Result
{Lemma}
{
%
\Disp{
\leq 
\tau_{s, s'}
\leq \delta_s
}
}

The rest follows ``The Dantzig Selector'' very closely.
\Result
{Proposition}
{
Let \(g\) and \(d\) be defined as above.
Then
%
\Disp{
\|d_{BC}\|_1
\leq \|d_{\MC{A}}\|_1 +\|g_{BC}\|_1
}
}

@@

\Result
{Lemma}
{
Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in ().
%
\Disp{
|\IP{ d, P(:, n_h) }|
\leq& 4 \sqrt{\log N_h},
\quad n_h =1, \dotsc, N_h^2.
}
%
}

\Result
{Lemma}
{
Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in ().
%
\Disp{
\|P^\H P d\|_\infty
\leq& 4 \sqrt{\log N_h},
\quad n_h =1, \dotsc, N_h^2.
}
%
}

@@

\Result
{Lemma}
{
Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in () with constant \(\delta\).
%
\Disp{
\|d_{\MC{A}}\|_2
\leq \F{1}{1-\delta} \|P^\H_{\MC{A}\MC{B}} P d\|_2 +\F{\delta}{(1-\delta) \sqrt{L}} \|d_{BC}\|_1
}
%
}

@@

\Result
{Lemma}
{
Let \(d\) be defined as above.
Then
%
\Disp{
\|d\|_2^2
\leq \|d_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|d_{\MC{C}}\|_1^2
}
%
}

\subsection{The Main Bound}

We can now formulate and prove the main bound of ours.
